SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
emcee code change
must update to other systems as well
update on Simona's comments

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group show many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
 However, this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,K05,V09,N13}.  
At present, the amount of substructure derived from flux-ratio anomalies
seems to be disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.[COMMENT ON LINE OF SIGHT EFFECTS?--LEON]
%
An alternative method for
the detection of substructure in gravitational lens galaxies, utilizing
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.

@@

The B1555+375 system was also observed with the \textit{Hubble Space Telescope
(\textit{HST})} in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
galaxy clearly stands out.}

@@

Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (see in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the non-detection of these
images.[REF B0128 PAPER?--LEON]

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{Our next step is to examine if an edge-on disk can cause similar perturbations in the stong lensing system like substructures which resulting in flux ratio anomalies within merging images. In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. Detail definition of mass profiles in {\tt gravlens} 
  can be found in \citet{Kee01}.}
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE). 
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is needed because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

\textbf{To obtain the optimum lens model, we explore the parameter space with the following steps: 
(1) Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position. The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
(2) Optimum model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec). Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
(3) Markov Chain Monte Carlo: After obtaining the optimum lens model, we run MCMC to explore the parameter space for the uncertainties.} 
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

The optimum model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
%Both of these models produce lensed images with positions and
%fluxes that are good matches to the radio observations.  
%While both of the two component models 
%the 2-SIE version has a somewhat
%better performance than the SIE+expdisk model in reproducing flux
%ratios. 
Tables 3 \& 4 show the comparison between radio data and model predicted image positions and flux ratios.  
\textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}
We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.

@@

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & SIE & Expdisk 		   
\\
\hline
$x$  	  & $-0.1818 (0.005)$	&$-0.1472 (0.003)$ 	  \\
$y$	  &$-0.1988 (0.005)$	&$-0.2057 (0.010)$	 \\

$b$ &$0.21 (0.01)$  & ...   \\
$\kappa_0$ & ... & $0.11 (0.01)$        \\  
$e$	  & $0.31(0.01)$	&$0.87 (0.01)$ \\
$\theta$ &$2.96 \degr (0.64 \degr)$ &$7.00\degr (0.70 \degr)$ \\
$r_s$	& ...  & $0.28 (0.005)$\\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

@@

\hline
	& MERLIN  & \multicolumn{2}{c}{Model}\\
		&5 GHz   & SIE-only & SIE+expdisk \\
\hline
$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$  \\ 
$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.17$ \\
$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $8.69$ \\

@@

In this letter, we \textbf{instead} focus on the effect that more complicated lens galaxy mass
distributions \textbf{have} on flux-ratio anomalies.
Traditionally, flux-anomalous lensed quasars \textbf{have been} radio-loud, initially discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux-ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showed that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This newly discovered edge-on disk provides a strong prior for our
lens modelling.  With \textbf{an additional disk component}, our models produce
matches to both the radio image positions and their flux-ratio, wheras
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux-ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.

@@

\section*{Acknowledgments}
S.V. is grateful to Dandan Xu for useful discussion on the nature of flux-ratio anomalies in high resolution numerical simulations.
L.V.E.K. is supported in part through an NWO-VICI career grant (project number 639.043.308).
\bibliographystyle{mn2e}
\bibliography{reference.bib}

>>>>

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group show many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
 However, this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations, with the less level of flux anomalies showing in simulation results \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.[OTHER POSSIBLE ORIGONS--SIMONA]
%
An alternative method for
the detection of substructure in gravitational lens galaxies, utilizing
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.

@@

The B1555+375 system was also observed with the \textit{Hubble Space Telescope
(\textit{HST})} in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
galaxy clearly stands out.}
\textbf{The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so 
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. This assumption on redshifts is needed for the lens modelling because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

@@

Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (see 
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the non-detection of these
images.[REF B0128 PAPER?--LEON]

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. The free parameters of the models are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$), and exponential disk: intrinsic central density ($kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$). Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
  We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE).

To obtain \textbf{the minimum $\chi^2$} [OR BEST-FIT MODEL?--JEN] lens model, we explore the parameter space with the following steps: 
\begin{itemize}
\item Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position. The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
\item Best-fit model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec). Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
\item Markov Chain Monte Carlo: After obtaining the best-fit lens model, we run MCMC to explore the parameter space for the uncertainties.
\end{itemize}
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

The best-fit model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
%Both of these models produce lensed images with positions and
%fluxes that are good matches to the radio observations.  
%While both of the two component models 
%the 2-SIE version has a somewhat
%better performance than the SIE+expdisk model in reproducing flux
%ratios. 
Tables 3 \& 4 show the comparison between radio data and model predicted image positions and flux ratios.  
\textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}

@@

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & SIE & Expdisk 		   
\\
\hline
$x$  	  & $-0.1818 \pm 0.005$	&$-0.1472 \pm 0.005$ 	  \\
$y$	  &$-0.1988 \pm 0.005$	&$-0.2057 \pm 0.006$	 \\

$b$ &$0.21 \pm 0.01$  & ...   \\
$\kappa_0$ & ... & $0.11 \pm 0.01$        \\  
$e$	  & $0.31\pm 0.01$	&$0.87 \pm 0.01$ \\
$\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
$R_s$	& ...  & $0.28 \pm 0.01$\\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

@@

\hline
	& MERLIN  & \multicolumn{2}{c}{Model}\\
		&5 GHz   & SIE-only & SIE+expdisk \\
\hline
$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\

@@

In this letter, we \textbf{instead} focus on the effect that more complicated lens galaxy mass
distributions \textbf{have} on flux-ratio anomalies.
Traditionally, flux-anomalous lensed quasars \textbf{have been} radio-loud, initially discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux-ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showed that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This newly discovered edge-on disk provides a strong prior for our
lens modelling.  With an additional disk component, our model 
matches to both the radio image positions and their flux-ratio, wheras
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux-ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.

@@

\section*{Acknowledgments}
S.V. is grateful to Dandan Xu for useful discussion.
L.V.E.K. is supported in part through an NWO-VICI career grant (project number 639.043.308).
\bibliographystyle{mn2e}
\bibliography{reference.bib}
